Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
Changes to experiment section mostly

We evaluated model performance for all three models with a range of
values for $\mu$, the mean prior parameter for regression parameters 
($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\}$). The number of topics for all
models was set to 50, the prior distributions of
$p\left(\alpha\right)$, $p\left(\alpha^{\prime}\right)$, and $p\left(\gamma\right)$ were gamma distributed with a shape parameter of 1
and a scale parameters of 1000.

>>>>

For all of these models, particular attention was payed to the settings of the
prior parameters for the regression coefficients. These parameters implement an
important form of regularization in HSLDA. In the setting where there are no negative
labels, a Gaussian prior over the regression parameters with a negative mean implements
a prior belief that missing labels are likely to be negative. We evaluated model performance 
for all three models with a range of values for $\mu$, the mean prior parameter for regression coefficients
($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\}$).

The number of topics for all
models was set to 50, the prior distributions of
$p\left(\alpha\right)$, $p\left(\alpha^{\prime}\right)$, and $p\left(\gamma\right)$ were gamma distributed with a shape parameter of 1
and a scale parameters of 1000.
